Ripple Consensus Review

### 2015-04-26 paper.tex
sp

    \item The global consensus ledger has inherently poor $O(n^2)$ scaling;
        even in the absense of a malicious attack the poor scalability of the
        ledger is a threat to the viability of Ripple.

>>>>

    \item The global consensus ledger has inherently poor $O(n^2)$ scaling;
        even in the absence of a malicious attack the poor scalability of the
        ledger is a threat to the viability of Ripple.
